Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-03-01 WRITEUP/ms.tex
shorten abs, shuttle context according to AF's oct suggestion, edits on instability sec

\usepackage{amsmath}
\input{preamble}
\slugcomment{Paper draft for the project developed at the Kavli Summer Program in Astrophysics 2018.
To be Submitted.}

@@

\begin{abstract}
We study the dynamical properties of molecular clouds complexes (MC) and their temporal evolution in a prototypical galaxy (\flower)
and its satellite galaxies at the Epoch of Reionization (EoR) using cosmological zoom-in simulation.
We use a clump-finding algorithm and H$_2$ density to identify MCs and their sub-structures.
We compare the mass, size, velocity dispersion, gas surface density, and virial parameter ($\alpha_{\rm vir}$)
of each MC with those observed in the Milky Way, the Galactic center,
and gas-rich starburst galaxies in the local Universe and at the peak epoch of cosmic \SF.
The high velocity dispersions found in the MCs of \flower ($\sigma\approx$\,200\,\kms) are comparable to
those observed in starburst galaxies.
The mass scale of the MCs is on the order of $10^{6.5-9}$\,\Msun.
The $\sim$200\,pc-scale MCs found with a low density threshold
correspond to the spiral arms of \flower which break down into smaller $\lesssim$100\,pc-scale MCs at higher density thresholds.
The velocity dispersion and gas surface density are found to be systematically higher than nearby galaxies
regardless of the $n_{\rm cut}$ adopted, with $\sigma\gtrsim$\,100\,\kms.
This likely results from the strong supernova and stellar feedback \flower experienced over multiple episodes of
bursty \SF and constant cosmic gas inflows.
Our results suggest that the more massive and bigger MCs of \flower compared to the Milky Way
likely result from the higher gas mass fraction, surface density, and velocity dispersion,
which together sets the scale for fragmentation.
Virial analysis indicates that the MCs found in the main disk of \flower are unbound, but its substructures have lower virial parameters,
 consistent with the notion that collapsing structures result from gravitational instability within globally stable structures, which are
supported by turbulence and rotation on large scale.
We find $\alpha_{\rm vir}\approx$\,2 for the MCs in the satellite galaxies, which we interpret as result of the weaker stellar feedback
due to the less frequency \SF compared to \flower (also supported by the lower stellar-to-gas mass ratio of the former).
High resolution imaging of the first galaxies with the Atacama Large (sub-)Millimeter Array (ALMA) and the
Next Generation Very Large Array (ngVLA)
will provide useful observational data to test our findings and the validity of our simulation to shed
light on \SF since the cosmic dark ages.
\end{abstract}
\keywords{methods: data analysis --
          galaxies: high-redshift --
          galaxies: ISM --
          galaxies: evolution --
          galaxies: formation --
          galaxies: starburst --
          stars: formation}

@@

The FIR fine-structure lines (e.g., \cii, \nii, and \oiii), and CO/[\ci]~lines are the key diagnostics for
constraining the ISM conditions of galaxies and
provide highly complementary information tracing the different phases of the ISM (ionized,
atomic, molecular; e.g., \citealt{Scoville74a, Rubin85a, Malhotra01a}).
Global measurements of these diagnostics in \highz galaxies
have informed us on their galaxy-wide properties (e.g.,
gas masses, gas temperature, and radiation field intensity).
However, spatially resolving their ISM is necessary to understand their roles in galaxy evolution and
the physics behind their intense \SF (SFR\ssim100$-$3000\,\Msun\,yr\pmOne).
To date, spatially resolved ISM properties of \highz galaxies
have only been examine observationally in a handful of (strongly-lensed)
galaxies, using tracers such as
dust continuum, CO, and \cii lines (e.g., \citealt{Swinbank11a, Hodge15a, Ferkinhoff15a, Hodge16a},
Leung et al. 2018, submitted).
These studies find that galaxies at $z$\ssim2 galaxies, close to the peak of cosmic \SF, are more
molecular gas-rich, turbulent, and clumpy than nearby galaxies.
That said, it remains unclear how \SF proceed in the (sub-)$L^*$ galaxy population at \z$\gtrsim$\,6 ---
the epoch of reionization  ---
which is responsible for producing the
ionizing photons that reionized the Universe.

While ALMA has enabled the detections of
ISM diagnostic lines e.g., the \cii158\,$\micron$ and CO line emission in
normal (SFR$<$\,100\,\Msun\,yr\pmOne) galaxies at \z$>$\,6 over the past few years \citep[e.g.,][]{Odorico18a, Carniani18b},
we are still far from mapping their molecular ISM due to the cosmological dimming.
As such, we have undertaken a study, exploiting
state-of-the-art cosmological zoom-in hydrodynamic simulation
\ncode{Serra} (Greenhouse in Italian; \citealt{Pallottini17a, Pallottini17b}), to examine
the dynamical properties of the molecular cloud complexes in a \z$\sim$6 prototypical (i.e., $L^*$)
galaxy.
{\bf AF: need aim and objectives of the study}

This paper is structured as follows.
% \AP{TBM}
In \Sec{sim}, we describe the setup of our simulation and properties of our main galaxy (\flower),
and describe the method used to identify its molecular gas complexes.
In \Sec{results}, we present scaling relations based on
the MC identified and compare them with observations of molecular clouds
and structures seen in nearby and \z$>$\,0 galaxies.
% We present Toomre stability analysis in \Sec{Q}.
We discuss the results % , robustness of our analysis, caveats,
and implications of our findings in \Sec{diss},
and present our conclusions in \Sec{conclusion}.
Throughout this paper, we adopt a concordance cosmology, with total matter, vacuum and baryonic densities
in units of the critical density $\Omega_{\Lambda}$\eq0.692, $\Omega_m$\eq0.308, $\Omega_b$\eq0.0481,
Hubble constant $H_0$\eq100\,$h$\,km s\pmOne\,Mpc\pmOne with $h$\eq0.678,
spectral index $n$\eq0.967 and $\sigma_8$\eq0.826 \citep{Planck14a}.

% ------------------
\section{Method: Simulation and ``Clump''-finding} \label{sec:sim}

@@

\ncode{Serra} is a cosmological zoom-in simulation performed using Eulerian hydrodynamics and
adaptive mesh refinement (AMR) technique to achieve high spatial resolution in the region of interest (i.e., regions of high density).
In particular, it uses a modified version of \ncode{ramses} \citep{Teyssier2002a} as the AMR backend.
Our simulation covers a co-moving box of 20\,Mpc $h$\pmOne in size, resolving down to a physical scale of $l\approx$\,30\,pc (at \z$\sim$\,6) and a (baryonic) mass resolution of $m_b\simeq$\,10$^4$\,\Msun at the finest level. Such a physical scale is close to the size scale of molecular cloud complexes and giant molecular clouds (GMCs) seen in nearby galaxies \citep[e.g.,][]{Sanders85a, Federrath13a, Goodman14a}.
We include chemical network in the simulation to trace $\rm{H}$, $\rm{H}^{+}$, $\rm{H}^{-}$, $\rm{He}$, $\rm{He}^{+}$, $\rm{He}^{++}$, $\rm{H}_2$, $\rm{H}_2^{+}$ \citep{Grassi14a,Bovino16a}.
Of particular importance to our study here is that our simulation includes non-equilibrium formation of molecular hydrogen (done on-the-fly) to determine the H$_2$ abundance (see \citealt{Pallottini17b} for effects of chemistry affected by non-equilibrium versus equilibrium H$_2$ formation).

@@

\subsection{Star Formation History} \label{sec:sfh}
One of the main advantages for studying the dynamical properties of molecular structures at
$z$\ssim6 in simulation is the fact that we can examine how their properties evolve
as a function of time.
% {\AP potentially moving the following, maybe postpone after structures have been identified as a description? }
% {\DL or maybe in the discussion section?}
This is advantageous especially at early cosmic epochs,
when the densest structures are beginning to form;
gas is constantly being accreted onto the central galaxy from the cosmic web and
satellite galaxies, thereby leading to bursts of \SF.
Meanwhile, tidal forces resulting from interactions with these surrounding
galaxies can disrupt the main disk and arms, likely leading to different dynamical states
for the molecular structures compared to more evolved galaxies found at
a later cosmic time (e.g., some molecular structures may disperse while others may agglomerate into more massive
ones). % mainly expecting differences in alpha_vir, sigma, M_cl.

@@

We show the \SF history of \flower in \Fig{SFH}, where
the SFR of \flower varies between $\sim$30$-$80\,\Msun\,yr\pmOne\footnote{
The SFR plotted in Figure 2 of \citet{Pallottini17b}
is a factor of two higher than shown here since they also include contributions from
massive satellite galaxies within the surrounding $\approx$50\,kpc, which
are accreted onto \flower at \z$\lesssim$\,2.}
as it evolves from an actively accreting phase to
a starburst phase after a major merger, and then back to a relatively quiescent phase
over the few hundred Myr simulated in our simulation.
The SFR of \flower is calculated based on existing young stellar population, which is
defined to have an age of $t_{\rm age}<$\,10\,Myr.

Given the stochasticity in the \SF history of \flower,
we show the scaling relations found for two particular snapshots/evolutionary stages of \flower
as examples in \Sec{singless} to illustrate the salient points of the discussion presented in this paper,
since they represent the extreme evolutionary stages of \flower (and thus, likely bracket the
most extreme variations in the cloud dynamics) --- one of which \flower is
actively accreting materials from its surrounding
and another of which \flower is undergoing
a starburst phase after a major merger (see \Fig{SFH}).

@@

\begin{figure*}[htbp]
 \centering
  \includegraphics[scale=0.65]{\figpath/{dual_16_ncut_0.53}.pdf}
  \\ [-2.9em]
  \includegraphics[scale=0.65]{\figpath/{dual_16_ncut_6.81}.pdf}
  \\ [-2.9em]
  \includegraphics[scale=0.65]{\figpath/{dual_16_ncut_18.96}.pdf}
\caption{
Examples showing the MCs identified in our simulation by applying volumetric H$_2$ density cuts of
$n_{\rm cut}$\eq[0.53, 6.81,19.00]\,cm$^{-3}$, which is only a subset of all the $n_{\rm cut}$ adopted (see text).
    Color shows the H$_2$ surface density, weighted by the column density.
%   \AP{plot a proper label for the colorbar, and remove the trailing right axes labels (that are still there despite our efforts)}\DL{I tried more on Sept 7th, errrr, now all the ticks and labels for both panels disappear... hmm.. Not worth my time to fix this for the report.}
\label{fig:MC}}
% \addtocounter{figure}{-1}
\end{figure*}

In \Fig{h2density}, we show an example of the volumetric H$_2$ density ($n_{\rm H2}$) distribution of \flower
for a given snapshot which includes contributions within $R\sim$\,3.5\,kpc from the galaxy center\footnote{For reference,
the half mass radius of \flower is $\sim$0.5\,kpc and the dark matter virial radius at which the mean enclosed density is 200 times
the critical density of the Universe % presumably defined at the redshift of \flower here?
is $r_{\rm 200}$\ssim15\,kpc.}.
We note that the distribution is almost flat for $n_{\rm H2}\gtrsim1$\,\cc and it samples the range of density
where ``clumps/structures'' are
found based on the Euler characteristic, i.e., the fourth Minkowsky functional (see \citealt{Pallottini17b}).
We identify MCs by applying 10 equally-spaced volumetric H$_2$ density cuts of
$\log{(n_{\rm cut}/{\rm cm^{-3})}}\in[-0.5, 1.5]$\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 19.00, 31.62]\footnote{We also vary the range of
$n_{\rm cut}$ adopted and find no qualitative differences
affecting the results and conclusions of this work except in the slope of the CMF (see \Sec{ncut} and \Sec{cmf}).}
to the same snapshot
used to plot \Fig{h2density}.

@@

\section{Results: Cloud Scaling Relations}     \label{sec:results}

%\AP{I see 2 main possible approaches to the presentation of the results
%%
%(a) focus on a single snapshot, analyze the cloud scaling relation by varying the cuts and then by varying the snapshot; after that one can discuss the stability/toomre analysis of the clumps (help in discussing the origin) and the CMF.
%%
%(b) discuss each scaling relation one at a time; probabily an introductionary subsection is needed to explain that different cuts yields no qualitative differences.
%%
%Note that -- in both cases -- alternatively toomre analysis can be done at the beginning of the result section(s).
%%
%I think that (b) might be a little bit more appealing, since all the plot with similar quantities (e.g. the larson relation for multiple cuts and snapshots) are in the same place (or, even better, page).
%}
%\DL{agreed, but will move things around later, after the report and after most of the content is ready.}

Molecular clouds are the natal place for \SF, and thus,
their structure and dynamics hold important clues to understanding
the mechanisms and physics of formation and evolution of molecular structures and \SF.
Upon identifying the molecular structures, we extract properties such as
mass ($M_{\rm cl}$),
size ($R$),
Mach number ($\mathcal{M}$), velocity dispersion ($\sigma$), and
gas surface density ($\Sigma_{\rm gas}$)
to examine their dynamics.

@@

We show in \Fig{dist} the MC distributions in terms of their
molecular gas masses, radii, and gas mass fractions, which we define as
\begin{equation}
f_{\rm gas} = \frac{M_{\rm H2}} {\left(M_{\rm H2} + M_*\right)},
\end{equation}
where $M_*$ is the stellar mass.
We note that the distributions vary for different snapshots, depending on the evolutionary stage of \flower.
The highest density threshold of $n_{\rm cut}$\eq31.62\,\cc yields a ``minimum'' MC mass of
the order of 10$^{6.5}$\,\Msun for the densest MC.
% {\AP  maybe we can tie it to the mass resolution limitation imposed by our criterion.}
We find $\sim$10$-$13 MCs with masses exceeding 10$^8$\,\Msun across all the
snapshots for each of the given $n_{\rm cut}$ (see \Sec{method}).

@@

We show in \Fig{MR} the size-mass relation of the MCs of \flower in its accretion phase (see \Sec{sfh})
compared to
observational data of molecular clouds in the Milky Way that are found to be associated with massive \SF
\citep{Beuther02a, Mueller02a, Hill05a, Motte07a} and an empirical relation obtained for massive \SF based on
Milky Way clouds ($<$10\,\Msun; \citealt{Kauffmann10b, Kauffmann10c} and references therein): $M \gtrsim 870$\,\Msun$\times\,\left(r/{\rm pc}\right)^{1.33}$.
\citet{Kauffmann10c} interpret this empirical relation
as the threshold for massive \SF.
The implication of this result is that cluster-forming cloud fragments are
found to be more massive than those that are devoid of clusters
at a given radius.
We also show the loci of constant surface densities in \Fig{MR}, parameterized through the visual extinction $A_V$.

>>>>

\usepackage{amsmath}
\input{preamble}
\slugcomment{To be Submitted.}

@@

\begin{abstract}
We study the dynamical properties of molecular clouds complexes (MC) in a prototypical galaxy (\flower)
and its satellite galaxies at the Epoch of Reionization (EoR) using cosmological zoom-in simulation.
We identify MCs using H$_2$ density, 
and compare their masses, sizes, velocity dispersions, gas surface densities, and virial parameters ($\alpha_{\rm vir}$)
with those observed in nearby and \z$\sim$\,2 galaxies.
The MCs span a mass range of $10^{6.5-9}$\,\Msun. Their velocity dispersions and gas surface densities are 
systematically higher than those observed in nearby galaxies but comparable to 
starburst galaxies, with $\sigma\gtrsim$\,100\,\kms.
This likely results from the strong supernova and stellar feedback \flower experienced over multiple episodes of
bursty \SF and cosmic gas inflows.
Our results suggest that the more massive and bigger MCs of \flower compared to the Milky Way
manifest from the higher gas mass fraction, surface density, and velocity dispersion.
% , which together sets the scale for fragmentation.
Virial analysis indicates that the MCs in the main disk of \flower are unbound, but its substructures have lower virial parameters,
consistent with the notion that collapsing structures result from gravitational instability within globally stable structures.
% , which are supported by turbulence and rotation on large scale.
We find $\alpha_{\rm vir}\approx$\,2 for the MCs in the satellite galaxies, which we interpret as result from the weaker stellar feedback
due to the less frequent \SF compared to \flower.
High resolution imaging of the first galaxies with the Atacama Large (sub-)Millimeter Array (ALMA) and the
Next Generation Very Large Array (ngVLA)
will furnish useful data to test our findings and simulation to shed
light on \SF since the cosmic dark ages.
\end{abstract}
\keywords{methods: data analysis --
          galaxies: high-redshift --
          galaxies: ISM --
          galaxies: evolution --
          galaxies: formation --
          galaxies: starburst --
          stars: formation}

@@

The FIR fine-structure lines (e.g., \cii, \nii, and \oiii), and CO and [\ci]~lines are the key diagnostics for
constraining the ISM conditions of a galaxy by
providing highly complementary information that trace different phases of the ISM (ionized,
atomic, molecular; e.g., \citealt{Scoville74a, Rubin85a, Malhotra01a}).
Global measurements of these diagnostics in \highz galaxies
have informed us on their galaxy-wide properties (e.g.,
gas masses, gas temperature, and radiation field intensity).
However, spatially resolving their ISM is necessary to understand their roles in galaxy evolution and
the physics behind their intense \SF (SFR\ssim100$-$3000\,\Msun\,yr\pmOne).
To date, spatially resolved ISM properties of \highz galaxies
have only been examine observationally in a handful of (strongly-lensed)
galaxies, using tracers such as
dust continuum, CO, and \cii lines (e.g., \citealt{Swinbank11a, Hodge15a, Ferkinhoff15a, Hodge16a, Leung19a}).
These studies find that galaxies at $z$\ssim2 galaxies, close to the peak of cosmic \SF, are more
molecular gas-rich, turbulent, and clumpy than nearby galaxies.
That said, it remains unclear how \SF proceed in the (sub-)$L^*$ galaxy population at \z$\gtrsim$\,6 ---
the epoch of reionization  ---
which is responsible for producing the
ionizing photons that reionized the Universe.
While ALMA has enabled the detections of
ISM diagnostic lines e.g., the \cii158\,$\micron$ and CO line emission in
normal (SFR$<$\,100\,\Msun\,yr\pmOne) galaxies at \z$>$\,6 over the past few years \citep[e.g.,][]{Odorico18a, Carniani18b},
we are still far from mapping their molecular ISM due to the cosmological dimming.
As such, we have undertaken a study, exploiting
state-of-the-art cosmological zoom-in hydrodynamic simulation
\ncode{Serra} (Greenhouse in Italian; \citealt{Pallottini17a, Pallottini17b}), with a goal to examine
and predict the dynamical properties of the star-forming molecular cloud complexes in a \z$\sim$6 prototypical (i.e., $L^*$)
galaxy. % to understand the physics behind \SF in the first galaxies.

This paper is structured as follows.
In \Sec{sim}, we describe the setup of our simulation and properties of our main galaxy (\flower),
and describe the method used to identify its molecular gas complexes.
In \Sec{eqn}, we present the formalism within which we interpret the results.
In \Sec{results}, we present scaling relations for the MCs identified. 
% Toomre stability analysis in \Sec{Q}.
We then interpret the results   % , robustness of our analysis, caveats,
and discuss the implications of our findings in \Sec{diss},
and present our conclusions in \Sec{conclusion}.
Throughout this paper, we adopt a concordance cosmology, with total matter, vacuum and baryonic densities
in units of the critical density $\Omega_{\Lambda}$\eq0.692, $\Omega_m$\eq0.308, $\Omega_b$\eq0.0481,
Hubble constant $H_0$\eq100\,$h$\,km s\pmOne\,Mpc\pmOne with $h$\eq0.678,
spectral index $n$\eq0.967 and $\sigma_8$\eq0.826 \citep{Planck14a}.

% ------------------
\section{Simulation and Method} \label{sec:sim}

@@

\ncode{Serra} is a suite of cosmological zoom-in simulations performed using Eulerian hydrodynamics and
adaptive mesh refinement (AMR) technique to achieve high spatial resolution in the region of interest (i.e., regions of high density).
In particular, it uses a modified version of \ncode{ramses} \citep{Teyssier2002a} as the AMR backend.
Our simulation covers a co-moving box of 20\,Mpc $h$\pmOne in size, resolving down to a physical scale of $l\approx$\,30\,pc (at \z$\sim$\,6) and a (baryonic) mass resolution of $m_b\simeq$\,10$^4$\,\Msun at the finest level. Such a physical scale is close to the size scale of molecular cloud complexes and giant molecular clouds (GMCs) seen in nearby galaxies \citep[e.g.,][]{Sanders85a, Federrath13a, Goodman14a}.
We include chemical network in the simulation to trace $\rm{H}$, $\rm{H}^{+}$, $\rm{H}^{-}$, $\rm{He}$, $\rm{He}^{+}$, $\rm{He}^{++}$, $\rm{H}_2$, $\rm{H}_2^{+}$ \citep{Grassi14a,Bovino16a}.
Of particular importance to our study here is that our simulation includes non-equilibrium formation of molecular hydrogen (done on-the-fly) to determine the H$_2$ abundance (see \citealt{Pallottini17b} for effects of chemistry affected by non-equilibrium versus equilibrium H$_2$ formation).

@@

\subsection{Star Formation History} \label{sec:sfh}
One of the main advantages for studying the dynamical properties of molecular structures at
$z$\ssim6 in simulation is the fact that we can examine how their properties evolve
as a function of time.
This is advantageous especially at early cosmic epochs,
when the densest structures are beginning to form;
gas is constantly being accreted onto the central galaxy from the cosmic web and
satellite galaxies, thereby leading to bursts of \SF.
Meanwhile, tidal forces resulting from interactions with these surrounding
galaxies can disrupt the main disk and arms, likely leading to different dynamical states
for the molecular structures compared to more evolved galaxies found at
a later cosmic time (e.g., some molecular structures may disperse while others may agglomerate into more massive
ones). % mainly expecting differences in alpha_vir, sigma, M_cl.

@@

We show the \SF history of \flower in \Fig{SFH},
where the SFR is calculated based on existing young stellar population, which is
defined to have an age of $t_{\rm age}<$\,10\,Myr.
The SFR of \flower varies between $\sim$30$-$80\,\Msun\,yr\pmOne\footnote{
The SFR plotted in Figure 2 of \citet{Pallottini17b}
is a factor of two higher than shown here since they also include contributions from
massive satellite galaxies within the surrounding $\approx$50\,kpc, which
are accreted onto \flower at \z$\lesssim$\,2.}
as it evolves from an actively accreting phase to
a starburst phase after a major merger, and then back to a relatively quiescent phase,
over the few hundred Myr simulated in the simulation.

Given the stochasticity in the \SF history of \flower (see \Fig{SFH}),
we show the scaling relations found for two snapshots, corresponding to two of its most extreme evolutionary stages,
in \Sec{singless} to illustrate the salient points of the discussion presented in this paper.
The two phases (when \flower is accreting materials from its surrounding 
and when \flower is undergoing a major starburst phase) are expected to bracket the most extreme variations in the cloud dynamics.

@@

\begin{figure*}[htbp]
 \centering
  \includegraphics[scale=0.6]{\figpath/{dual_16_ncut_0.53}.pdf}
  \\ [-2.9em]
  \includegraphics[scale=0.6]{\figpath/{dual_16_ncut_6.81}.pdf}
  \\ [-2.9em]
  \includegraphics[scale=0.6]{\figpath/{dual_16_ncut_18.96}.pdf}
\caption{
Examples showing the MCs identified in our simulation by applying volumetric H$_2$ density cuts of
$n_{\rm cut}$\eq[0.53, 6.81,19.00]\,cm$^{-3}$, which is only a subset of all the $n_{\rm cut}$ adopted (see text).
    Color shows the H$_2$ surface density, weighted by the column density.
%   \AP{plot a proper label for the colorbar, and remove the trailing right axes labels (that are still there despite our efforts)}\DL{I tried more on Sept 7th, errrr, now all the ticks and labels for both panels disappear... hmm.. Not worth my time to fix this for the report.}
\label{fig:MC}}
% \addtocounter{figure}{-1}
\end{figure*}

In \Fig{h2density}, we show an example of the volumetric H$_2$ density ($n_{\rm H2}$) distribution of \flower
for a given snapshot which includes contributions within $R\sim$\,3.5\,kpc from the galaxy center\footnote{For reference,
the half mass radius of \flower is $\sim$0.5\,kpc and the dark matter virial radius at which the mean enclosed density is 200 times
the critical density of the Universe % presumably defined at the redshift of \flower here?
is $r_{\rm 200}$\ssim15\,kpc.}.
We note that the distribution is almost flat for $n_{\rm H2}\gtrsim1$\,\cc and it samples the range of density
where ``clumps/structures'' are
found based on the Euler characteristic, i.e., the fourth Minkowsky functional (see \citealt{Pallottini17b}).
We identify MCs by applying 10 equally-spaced volumetric H$_2$ density cuts of
$\log{(n_{\rm cut}/{\rm cm^{-3})}}\in[-0.5, 1.5]$\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 19.00, 31.62]\footnote{We also vary the range of
$n_{\rm cut}$ adopted and find no qualitative differences
affecting the results and conclusions of this work except in the slope of the CMF (see \Sec{ncut}).}
to the same snapshot
used to plot \Fig{h2density}.

@@

\section{Basic Physics} \label{sec:eqn}
\subsection{Virial Equilibrium and Larson's Relations}  \label{sec:PVE}
% \AP{I fear that putting this subsection here breaks a bit the flow of the analysis of the results. Maybe we can put it as an appendix and keep only eq. 10 in the main text (a put it at when analysing the relevant plot)? }

% Relating Larson's law to stability and pressure (perhaps move this to other section?).
A spherically symmetric cloud of mass $M$ and radius $R$ embedded within
a medium of pressure $P$ is described using the virial theorem:
\begin{equation}
\frac{1}{2}\ddot I = 2(T - T_s) + W + B,
\end{equation}
where $\ddot I$ is the second time derivative of the Lagrangian moment of inertia,
$T$ is the volume term of the total kinetic energy (including thermal and
bulk motions), $T_s$ is the surface term due to external pressure,
$W$ is the gravity term, and $B$ is the magnetic term.
In the case where magnetic field is excluded (i.e., $B$\eq0), we can express this in terms of:
\begin{equation}
\frac{1}{2}\ddot I = 3 M \sigma^2 - \frac{\Gamma GM^2}{R} - 4\pi P_{\rm ext} R,
\label{eqn:virial}
\end{equation}
where the first term on the right hand side (RHS) is the pressure term from velocity dispersion, the second
term is the gravity term, and the third term is the external pressure term.
For the case of simple virial equilibrium (SVE; i.e., equilibrium state without external pressure),
the LHS and the last term on the RHS vanish. The equation becomes:
\begin{equation}
\alpha_{\rm vir} = \frac{3\sigma^2}{\Gamma GM/R} = \frac{5\sigma^2R}{GM},
\label{eqn:alpha}
\end{equation}
where $\Gamma$ is set to 3/5 for a uniform sphere.
We can define
\begin{equation}
V_0^2\equiv\frac{\sigma^2}{R},
\end{equation}
which is related to one of the Larson's relations (linewidth-size relation),
which can be recast into the form of:
\begin{equation}
\sigma^2/R = \pi G \Sigma/5.
\end{equation}
For pressure-bounded virial equilibrium (PVE; i.e. equilibrium state with pressure), % external pressure
Equation~\ref{eqn:virial} becomes:
\begin{equation}
P_{\rm ext} = \frac{3\sigma^2M}{4\pi R^3} - \frac{\Gamma G M^2}{4\pi R^4},
\label{eqn:pext}
\end{equation}
which describes the external pressure needed to confine the gas inside a volume $V$.
Rearranging the equation and substituting $\Sigma$\eq$M/\pi R^2$, we can express
this equation using the following:
\begin{equation}
\frac{\sigma^2}{R} = \frac{1}{3}\left(\frac{4P_{\rm ext}}{\Sigma} + \Gamma G \Sigma \pi \right).
\label{eqn:v0}
\end{equation}
Therefore, for a virialized cloud, one expects a one-to-one mapping between $V_0^2$ and $\Sigma$ since
$\sigma^2/R\propto\Sigma$, whereas
Equation~\ref{eqn:v0} represents the loci along which external pressures $P_{\rm ext}$ are
needed in order for MCs to have linewidths $\sigma$ for a given set of surface densities. % (see\Fig{alpha27}).
In other words, a cloud with $\sigma$ and $\Sigma$ offset from $\sigma^2/R\mapsto\Sigma$
is in equilibrium with the external pressure $P_{\rm ext}$ (and therefore $V_0^2$ is not constant with $\Sigma$ but
varies depending on $P_{\rm ext}$; cf. expectation for SVE, where
$\sigma\propto R^{0.5}$; see e.g., \citealt{Heyer09a, Hughes10a, Hughes13b, Meidt13a}).

\subsection{Gravitational Instabilities}   \label{sec:Q}
The onset of gravitational instability is considered to be tightly connected to \SF \citep[e.g.,][]{Kennicutt89a, Wang94a, Li05b, Li06a}.
From virial theorem, the Jeans 
instability sets the scales at which gravitational potential overcomes kinetic energy. Namely, gravitational instabilities 
dominates at scales $L > L_J$, where $L_J$ is the Jeans length. 
However, in a differentially rotating system, centrifugal force resulting from differential rotation can 
inhibit collapse even on these scales. Thus, a disk is unstable in the regime of $L_J < L < L_{\rm rot}$, where $L_{\rm rot}$ is set 
% \propto \Sigma/B^2
by the surface density of the disk and the angular velocity of the rotation.

In theoretical and observational works, gravitational instability has been widely discussed in the 
context of the Toomre stability criterion \citep{Toomre64a, Goldreich65b}, or the Toomre Q parameter 
(or the proxy, circular velocity to dispersion ratio; $v_{\rm circ}/\sigma$; e.g., \citealt{GarciaBurillo03a, Genzel11a, Kassin12a, Leung19a}).
% https://ned.ipac.caltech.edu/level5/March15/Glazebrook/Glazebrook5.html
%
% from linear analysis
For {\it axisymmetric} mode ($m$\eq0), the dispersion relation for the growth of density perturbation in a rotating turbulent disk
of finite thickness $h$ 
is described by:
\begin{equation}
\omega^2 = \kappa^2 - \frac{2\pi G \Sigma |k|}{1 + |k| h} + \sigma^2 k^2,
\label{eqn:3Ddisp}
\end{equation}
where $k$ is the wavenumber and $\kappa$ is the epicyclic frequency, defined as:
\begin{equation}
\kappa^2\equiv\frac{2\Omega}{R}\frac{d}{dR}\left(R^2\Omega\right).
\label{eqn:kappa}
\end{equation}
% \kappa\propto\Omega
The first term on the RHS of Equation~\ref{eqn:3Ddisp} describes rotation support, whereas the second term describes self-gravity, and
the third term describes pressure support.
One can then define the so-called Toomre-Q parameter as:
\begin{equation}
Q\equiv\frac{\sigma\kappa}{\pi G \Sigma}.
\label{eqn:Q}
\end{equation}
For a thin disk, where $kh\ll1$, Equation~\ref{eqn:3Ddisp} reduces to the thin disk approximation, which 
becomes unstable % perturbation grows exponentially in time
for some $k$ when $\omega^2 < 0$ (or equivalently, $Q < 1$; \citealt{Toomre64a}).
Under this condition (i.e., when local gravitational instability 
overcomes support from pressure and rotation), fragmentation {\it can} happen. 
% but further evolution depends on their EOS.
%(e.g., instability impose by angular momentum from gas accretion from the cosmic web and
%satellite galaxies and stellar feedback).
Similarly, for a collisionless fluid, the Toomre Q parameter is defined by:
\begin{equation}
Q\equiv\frac{\sigma\kappa}{3.36 G \Sigma}
\end{equation}
\citep{Toomre64a}.

To account for stabilizing effect of both gas and stars and the non-negligible disk thickness, 
% since thickness of a disk weakens the gravitational forces within the disk plane and lower the values for $Q$
% Romeo:  The effect of thickness is to increase the stability parameter of each 
% component by a factor T, which depends on the ratio of vertical to radial velocity dispersion, following eqn 8 of their paper.
we consider the approximation for the effective two-component $Q_{\rm eff}$ parameter following \citet{Romeo11a} which is 
expressed as follows:
\begin{equation}
Q^{-1}_{\rm eff} = \[ \left\{
				\begin{array}{lccr}
					     {\displaystyle\frac{w}{T_{\rm star} Q_{\rm star}} + \frac{1}{T_{\rm gas} Q_{\rm gas}}}      & & & \mbox{if\ }T_{\rm star} Q_{\rm star} \geq T_{\rm gas} Q_{\rm gas} \\ [0.75em]
                                               {\displaystyle\frac{1}{T_{\rm star} Q_{\rm star}} + \frac{w}{T_{\rm gas} Q_{\rm gas}}}      & & & \mbox{if\ }T_{\rm star} Q_{\rm star} \leq T_{\rm gas} Q_{\rm gas} \\				
				\end{array} 
			    \right,
			    \]
\end{equation}
where $w$ is defined as:
\begin{equation}
w\equiv\frac{2 \sigma_{\rm star} \sigma_{\rm gas}}{\sigma_{\rm star}^2 + \sigma_{\rm gas}^2},
\end{equation}
and $T$ is defined as:
\begin{equation}
T\approx
0.8+0.7\left(\frac{\sigma_{z}}{\sigma_{R}}\right)\,.
\end{equation}

\subsection{Key Properties of Clouds}

% Molecular clouds are the natal place for \SF, their structure and dynamics hold important clues to understanding
% the mechanisms and physics of formation and evolution of molecular structures and \SF.
In next section, we examine the MC properties in the context of the Larson's relations \citep{Larson81a}, which
describe interactions between gravity and turbulence and is the first set of
relations used for studying star-forming molecular structure formation based on observables (linewidth-size,
density-size, and mass-size relations) and for comparing properties of molecular structures
in different galactic environments.
% Inner MW: R=2-8.5 kpc, most of the mass in the molecular ISM is in the form of GMCs with sizes $gtrsim$20\,pc and masses greater than 10$^5$\,\Msun \citep{Sanders85a}.

Upon identifying the molecular structures, we extract properties such as
mass ($M_{\rm cl}$),
size ($R$),
Mach number ($\mathcal{M}$), velocity dispersion ($\sigma$), and
gas surface density ($\Sigma_{\rm gas}$)
to examine their dynamics.

@@

We show in \Fig{dist} the MC distributions in terms of their
molecular gas masses, radii, and gas mass fractions, which we define as
\begin{equation}
f_{\rm gas} = \frac{M_{\rm H2}} {\left(M_{\rm H2} + M_*\right)},
\end{equation}
where $M_*$ is the stellar mass.
We note that the distributions vary for different snapshots, depending on the evolutionary stage of \flower.
The highest density threshold of $n_{\rm cut}$\eq31.62\,\cc yields a ``minimum'' MC mass of
the order of 10$^{6.5}$\,\Msun for the densest MC.
% {\AP  maybe we can tie it to the mass resolution limitation imposed by our criterion.}
We find $\sim$10$-$13 MCs with masses exceeding 10$^8$\,\Msun across all the
snapshots for each of the given $n_{\rm cut}$ (see \Sec{method}).
The mass of the MCs identified ranges between $M_{\rm cl}\approx$10$^{6.5-9}$\,\Msun, 
consistent with those observed in \z$\sim$2 galaxies in
rest-frame {\it UV and optical light} \citep{Elmegreen07a, Elmegreen09a}.

@@

We show in \Fig{MR} the size-mass relation of the MCs of \flower % in its accretion phase 
compared to
observational data of molecular clouds in the Milky Way that are found to be associated with massive \SF
\citep{Beuther02a, Mueller02a, Hill05a, Motte07a} and an empirical relation obtained for massive \SF based on
Milky Way clouds ($<$10\,\Msun; \citealt{Kauffmann10b, Kauffmann10c} and references therein): $M \gtrsim 870$\,\Msun$\times\,\left(r/{\rm pc}\right)^{1.33}$.
In the same plot, we also show loci of constant surface densities, which are parameterized through the visual extinction $A_V$.
As shown in \Fig{MR}, the MCs identified 
% in the accretion phase of 
in \flower lie above this relation, along the locus
with a visual extinction of $A_V$\eq4\,mag \citep{Lombardi10a}.
We discuss this result in the following section.
